Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny3

We have revised the manuscript ``Hydrodynamics of a semipermeable inextensible membrane under flow and confinement"  
by Bryan Quaife, Ashley Gannon, and Y.-N. Young, 
based on 
the referees' very helpful feedback.  
Thanks to the referees' comments
and suggestions, we believe the revised manuscript is much
improved. 
In the revised manuscript we ensure that
all of their concerns and questions are properly addressed.
Below is a summary of the revisions made in the new manuscript.
The detailed {\bf Response:}s to comments of referees are listed in 
{\bf Response:} to Referee 1 and Referee 2.
We hope that the referees and the
editor will now find the paper suitable for publication in 
Physical Review Fluids.

\vspace{0.5cm}
{\large \bf List of changes}
In the following we refer to Referee 1 who has five comments and Referee
2 who has three comments. In the revised manuscript the modifications in
the text are in blue.

@@

\noindent
{\bf Response:}: We thank the referee for this question. The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction. Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction). This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.

>>>>

We have revised the manuscript ``Hydrodynamics of a semipermeable inextensible membrane under flow and confinement"  
by Bryan Quaife, Ashley Gannon, and Y.-N. Young, 
based on 
the referees' very helpful feedback.  
Thanks to the referees' comments
and suggestions, we believe the revised manuscript is much
improved. 
In the revised manuscript we ensure that
all of their concerns and questions are properly addressed.
Below is a summary of the revisions made in the new manuscript.
The detailed responses to comments of referees are listed in 
responses to Referee 1 and Referee 2.
We hope that the referees and the
editor will now find the paper suitable for publication in 
Physical Review Fluids.

\vspace{0.5cm}
{\large \bf List of changes}
In the following we refer to Referee 1 who has five comments and Referee
2 who has three comments. In the revised manuscript the modifications in
the text are in magenta.

@@

\noindent
{\bf Response:}: We thank the referee for this question. The referee is indeed correct that in a 2D system the system remains constant in the $z$ direction. A two-dimensional vesicle membrane is a tube that is infinitely long in the $z$ direction.
On this infinitely long tube (constant in $z$), the line tension is the total tangential force along the circumferential surface. Divide this line tension by the length of the tube would give us the membrane tension (force per unit length) in the $x-y$ plane.  
%
%Consequently it is customary to focus on the 2D system on a plane, and the membrane tension is the membrane force per unit length (the length in the $z$ direction). This means that, after the division by the length in the third ($z$) direction, the membrane tension in the plane is force per length.
